Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-13 Paper.Rmd
cleaned code for extinction risk on LCohen model

- Ricker model (r $\neq$ 0):

    * For ricker model when extinction risk calculated after $25$ years, was plotted against each varying $d$ (=degree of dispersion), we found that extinction risk was higher for data came from left tail dependent environmental fluctuations than right tail dependent one upto $r=0.7$. For $r>0.7$, extinction risk is greater for data came from right tail dependent environmental fluctuations. [see Fig. \ref{fig_risk_local_disp} - \ref{fig_risk_global_disp}]

    * With increasing $K$ from $50$ to $200$, extinction risk in both case gets decreased as expected. [see Figure \ref{fig_risk_K_effect}]

With increasing number of patches from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Fig. \ref{fig_risk_numlocs_effect_local_disp} - Fig. \ref{fig_risk_numlocs_effect_global_disp}] for both model. -->

>>>>

-->

### 2019-02-13 SupportingInformation.Rmd
cleaned code for extinction risk on LCohen model

```{r tab_plankton_info, echo=F, results='asis',message=F}
library(tibble)
plankton_info <- tibble(c('Calanus I-IV','Para-Pseudocalanus spp','Temora longicornis','Acartia spp',
                          'Centropages typicus',
                          'Oithona spp','Echinoderm larvae','Calanus finmarchicus',
                          'Calanus helgolandicus','Metridia lucens','Decapoda larvae',
                   'Euphausiacea','Thalassiosira spp','Rhizosolenia styliformis',
                   'Ceratium fusus','Ceratium furca','Ceratium tripos','Ceratium macroceros',
                   'Rhizosolenia alata alata','Pseudocalanus elongatus Adult',
                   'Nitzschia delicatissima','Nitzschia seriata')
)
knitr::kable(plankton_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 22 plankton taxa for which data were available \\label{tab_plankton_info}",
      col.names = c("Plankton taxon name"))
```
<!--***DAN: These names differ from those used in Emma's 2016 Glob Change Biol paper.
Need to check with Chris Reid. Have to get this right.-->

@@

#source("mydispersal.R")
#set.seed(seed)

#rlist<-c(0,0.05,0.25,0.5,0.7,0.75,0.9,1.0,1.25,1.5,1.75,1.95)

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
#pdf("./Results/ext_risk_local_disp.pdf",heigh=6,width=10)
#op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
#for(r in rlist){
    #cat("r=",r,"\n")
#    s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
#    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
#    lines(s$d_seq,s$risk_right,type="b",col="blue")
#    legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
#    mtext(paste0("r = ", r))
#}
#par(op)
#dev.off()

# plot for global dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
#pdf("./Results/ext_risk_global_disp.pdf",heigh=6,width=10)
#op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
#for(r in rlist){
  #cat("r=",r,"\n")
#  s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
#  plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
#  lines(s$d_seq,s$risk_right,type="b",col="blue")
#  legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
#  mtext(paste0("r = ", r))
#}
#par(op)
#dev.off()

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
#pdf("./Results/ext_risk_numlocs_effect_local_disp.pdf",heigh=6,width=6)
#op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
#for(r in c(0,0.25)){
  #cat("r=",r,"\n")
#  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
#  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=F,ploton=F)

#  plot(s5$d_seq,s5$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#  lines(s25$d_seq,s25$risk_left,type="b",col="orange")
#  legend("topleft", title=paste0("r=",r," , left tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('red', 'orange'),  horiz=F, bty='n')

#  plot(s5$d_seq,s5$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",
#       panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#  lines(s25$d_seq,s25$risk_right,type="b",col="skyblue")
#  legend("topleft",title=paste0("r=",r," , right tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')
  #mtext(paste0("B",1))
#}
#par(op)
#dev.off()

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
#pdf("./Results/ext_risk_numlocs_effect_global_disp.pdf",heigh=6,width=6)
#op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
#for(r in c(0,0.25)){
  #cat("r=",r,"\n")
#  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
#  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=T,ploton=F)

#  plot(s5$d_seq,s5$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#  lines(s25$d_seq,s25$risk_left,type="b",col="orange")
#  legend("topleft", title=paste0("r=",r," , left tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('red', 'orange'),  horiz=F, bty='n')

#  plot(s5$d_seq,s5$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",
#       panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#  lines(s25$d_seq,s25$risk_right,type="b",col="skyblue")
#  legend("topleft",title=paste0("r=",r," , right tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')
  #mtext(paste0("B",1))
#}
#par(op)
#dev.off()

# plot to see the effect of K for r=0.25 (Ricker model)
#pdf("./Results/ext_risk_K_effect.pdf",heigh=6,width=6)
#op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)

#s1<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=50,disp_everywhere=F,ploton=F)
#s2<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=200,disp_everywhere=F,ploton=F)

#s3<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=50,disp_everywhere=T,ploton=F)
#s4<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=200,disp_everywhere=T,ploton=F)

#plot(s1$d_seq,s1$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#lines(s2$d_seq,s2$risk_left,type="b",col="orange")
#legend("topleft",title=("Noise : left tail dep., local disp."), c("K=50","K=200"), fill=c('red', 'orange'),  horiz=F, bty='n')

#plot(s1$d_seq,s1$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#lines(s2$d_seq,s2$risk_right,type="b",col="skyblue")
#legend("topleft",title=("Noise : right tail dep., local disp."),c("K=50","K=200"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')

#plot(s3$d_seq,s3$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#lines(s4$d_seq,s4$risk_left,type="b",col="orange")
#legend("topleft",title= ("Noise : left tail dep., global disp."),c("K=50","K=200"), fill=c('red', 'orange'),  horiz=F, bty='n')

#plot(s3$d_seq,s3$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
#lines(s4$d_seq,s4$risk_right,type="b",col="skyblue")
#legend("topleft",title=("Noise : right tail dep., global disp."),c("K=50","K=200"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')

#par(op)
#dev.off()
```

>>>>

```{r tab_plankton_info, echo=F, results='asis',message=F}
library(tibble)
plankton_info <- tibble(c1=c('Calanus stages I-IV','Para-pseudocalanus spp.','Temora longicornis','Acartia sp.',
                          'Centropages typicus',
                          'Oithona sp.','Echinoderm larvae','Calanus finmarchicus',
                          'Calanus helgolandicus','Metridia lucens','Decapoda larvae',
                   'Euphausiids','Thalassiosira sp.','Rhizosolenia styliformis',
                   'Ceratium fusus','Ceratium furca','Ceratium tripos','Ceratium macroceros',
                   'Proboscia alata','Pseudocalanus sp.',
                   'Pseudo-nitzschia delicatissima','Pseudo-nitzschia seriata')
)
cns<-c('Echinoderm larvae','Euphausiids','Decapoda larvae')
'%ni%' <- Negate('%in%')
idn<-which(plankton_info$c1%ni%cns)
knitr::kable(plankton_info, "latex", booktabs = T, linesep = "",
      caption = "Species names of 22 plankton taxa for which data were available \\label{tab_plankton_info}",
      col.names = c("Plankton taxon name"))%>%row_spec(row=idn,italic=T)
```
<!--***DAN: These names differ from those used in Emma's 2016 Glob Change Biol paper.
Need to check with Chris Reid. Have to get this right.-->

@@

source("mydispersal.R")
set.seed(seed)

model<-"lcohen"
numsims<-10000
numsteps<-25
params<-0
ext_thrs<-1
scl<-1
p0<-50

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/lcohen_ext_risk_local_disp.pdf",heigh=5,width=10)
op<-par(mfrow=c(1,2),mar=c(5,5,1.8,0.2),mgp=c(3,1,0))
s<-varying_d(numsims=numsims,numsteps =numsteps,numlocs=5,p0=p0,params=params,
                 ext_thrs=ext_thrs,scl=scl,model=model,disp_everywhere=F,ploton=F)
s1<-varying_d(numsims=numsims,numsteps =numsteps,numlocs=25,p0=p0,params=params,
                 ext_thrs=ext_thrs,scl=scl,model=model,disp_everywhere=F,ploton=F)
plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="black",
     xlab="d",ylab="Extinction risk",
     cex.lab=1.5,cex.axis=1.5,cex=1,pch=16,lwd=1.5)
lines(s1$d_seq,s1$risk_left,type="b",lwd=1.5,cex=1,pch=1)
legend(x=0.3,y=0.9, title=paste0("r = ",params," , left tail dep. in noise"), c("numlocs = 5","numlocs = 25"), 
       pch=c(16,1), lty=c(1,1),
       horiz=F, bty='n')

plot(s$d_seq,s$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="grey",
     xlab="d",ylab="Extinction risk",
     cex.lab=1.5,cex.axis=1.5,cex=1,pch=16,lwd=1.5)
lines(s1$d_seq,s1$risk_right,type="b",lwd=1.5,cex=1,pch=1,col="grey")
legend(x=0.3,y=0.9, title=paste0("r = ",params," , right tail dep. in noise"), c("numlocs = 5","numlocs = 25"), 
       pch=c(16,1), lty=c(1,1), col=c("grey","grey"),
       horiz=F, bty='n')

par(op)
dev.off()

# plot for global dispersal in D matrix 
# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/lcohen_ext_risk_global_disp.pdf",heigh=5,width=10)
op<-par(mfrow=c(1,2),mar=c(5,5,1.8,0.2),mgp=c(3,1,0))
s<-varying_d(numsims=numsims,numsteps =numsteps,numlocs=5,p0=p0,params=params,
                 ext_thrs=ext_thrs,scl=scl,model=model,disp_everywhere=T,ploton=F)
s1<-varying_d(numsims=numsims,numsteps =numsteps,numlocs=25,p0=p0,params=params,
                 ext_thrs=ext_thrs,scl=scl,model=model,disp_everywhere=T,ploton=F)
plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="black",xlab="d",ylab="Extinction risk",
     cex.lab=1.5,cex.axis=1.5,cex=1,pch=16,lwd=1.5)
lines(s1$d_seq,s1$risk_left,type="b",lwd=1.5,cex=1,pch=1)
legend(x=0.3,y=0.9, title=paste0("r = ",params," , left tail dep. in noise"), c("numlocs = 5","numlocs = 25"), 
       pch=c(16,1), lty=c(1,1),
       horiz=F, bty='n')

plot(s$d_seq,s$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="grey",xlab="d",ylab="Extinction risk",
     cex.lab=1.5,cex.axis=1.5,cex=1,pch=16,lwd=1.5)
lines(s1$d_seq,s1$risk_right,type="b",lwd=1.5,cex=1,pch=1,col="grey")
legend(x=0.3,y=0.9, title=paste0("r = ",params," , right tail dep. in noise"), c("numlocs = 5","numlocs = 25"), 
       pch=c(16,1), lty=c(1,1), col=c("grey","grey"),
       horiz=F, bty='n')
